Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2018-09-06 paper/tidy-missing-data-paper.Rmd
remove extra parenthesis
update vis_miss to use PNG to avoid strange printing behaviour

Tidy data [@Wickham2014] is a relatively new principle and suite of tools that
facilitate the process of converting raw data into a clean, analysis-ready
format that works efficiently in a data analysis pipeline. In tidy data, missing
values can be handled implicitly or explicitly, at the analyst's discretion.
However, when making a plot, missing values are simply dropped, albeit with a
warning (see Figure \@ref(fig:warning))). Most other analysis software will
simply drop cases with missings without warning.

@@

```{r vis-miss, fig.height = 4, fig.width = 6, out.width = "95%", fig.show = 'hold', echo = FALSE, fig.cap = "Heatmap visualizations of missing data for the airquality dataset. (A) The default output and (B) ordered by clustering on rows and columns. There are only missings in ozone and solar radiation, and there appears to be some structure to their missingness."}

@@

```{r applic-vis-miss, fig.height = 5, fig.width = 6.25, out.width = "85%", fig.show='hold', fig.cap = "Heatmap of clustered missingness for the housing data. Three groups of missingness are apparent, at the top for building area to longitude, the middle for building area and year built, at the end for building area, year built, and landsize. There is some structure in the missings."}

>>>>

Tidy data [@Wickham2014] is a relatively new principle and suite of tools that
facilitate the process of converting raw data into a clean, analysis-ready
format that works efficiently in a data analysis pipeline. In tidy data, missing
values can be handled implicitly or explicitly, at the analyst's discretion.
However, when making a plot, missing values are simply dropped, albeit with a
warning (see Figure \@ref(fig:warning)). Most other analysis software will
simply drop cases with missings without warning.

@@

```{r vis-miss, fig.height = 4, fig.width = 6, out.width = "95%", fig.show = 'hold', echo = FALSE, dev = "png", dpi = 300, fig.cap = "Heatmap visualizations of missing data for the airquality dataset. (A) The default output and (B) ordered by clustering on rows and columns. There are only missings in ozone and solar radiation, and there appears to be some structure to their missingness."}

@@

```{r applic-vis-miss, fig.height = 5, fig.width = 6.25, out.width = "85%", fig.show='hold', fig.cap = "Heatmap of clustered missingness for the housing data. Three groups of missingness are apparent, at the top for building area to longitude, the middle for building area and year built, at the end for building area, year built, and landsize. There is some structure in the missings.", dev = "png", dpi = 300}
